---
title: "HW4"
author: "Fiona Miller, Starry Zhou"
date: "April 4, 2017"
output:
  pdf_document: default
  html_document: default
---
```{r, message=FALSE, warning=FALSE}
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
```

```{r, include=FALSE}
class(db)
```

```{r, results='hide'}
db %>%
  dbGetQuery("SELECT * FROM kind_type;")
```

```{r, results='hide'}
db %>%
  dbGetQuery("SELECT * FROM info_type;")
```

```{r, results='hide'}
db %>%
  dbGetQuery("SELECT * FROM movie_info
             WHERE info_type_id = 3
             AND info = 'Western';")
```


## Problem 1
Compute the number of all films for each production_year. Your result should be a data.frame with two columns: production_year and num_films. something

```{r, results='hide'}
table <- db %>%
  dbGetQuery("SELECT * FROM title
             WHERE kind_id = 1;")

```

```{r,results='hide'}
problem1 <-table %>%
  group_by(production_year) %>%
  summarise(num_films = sum(n()))
```

```{r}
problem1
```


## Problem 2
Compute the number of Westerns for each production_year. Your result should be a  data.frame with two columns: production_year and num_westerns.
```{r, results='hide'}
table2 <- db %>%
  dbGetQuery("SELECT * FROM movie_info
             WHERE info_type_id = 3
             AND info = 'Western';")
```

```{r, results='hide'}
table3 <- db %>%
  dbGetQuery("SELECT * FROM title
             WHERE kind_id = 1;")
```

```{r, results='hide'}
table4 <- table2 %>%
  left_join(table3, by = c("movie_id" = "id"))
head(table4)
```

```{r,results='hide'}
problem2 <- table4 %>%
  group_by(production_year) %>%
  summarise(num_westerns = sum(n()))
```

```{r}
problem2
```

## Problem 3
Join the results from the previous two questions on production_year (using dplyr – not SQL). Compute the percentage of movies in each year that are Westerns.

```{r,results='hide'}
table5 <- problem1 %>%
  right_join(problem2, by = "production_year")
```

```{r,results='hide'}
problem3 <- table5%>%
  mutate(percentage=num_westerns/num_films*100)
```

```{r}
problem3
```



## Problem 4
Plot the percentage of films that are Westerns as a time series. Annotate your plot with the year in which Unforgiven was made. Do you find any evidence to suggest that Unforgiven revived the Western?

```{r,results='hide'}
problem3%>%
  filter(production_year=="1992")
```

```{r,results='hide', warning=FALSE}
problem4 <- ggplot(problem3, aes(x=production_year,y=percentage))+
geom_line(aes(fill = percentage))+
geom_point(aes(x=1992,y=0.2479632), size = 3, color = "red")+
annotate("text",x=1992,y=1,label="The year in which Unforgiven was made", size=3)
```

```{r, warning=FALSE}
problem4
```

